---
title: "Fourth Sunday after the Epiphany"
output:
  slidy_presentation:
    css: slide-style.css
---
  

```{r, include=FALSE}
knitr::opts_knit$set(root.dir = '../../') 
```

   
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

## A Mighty Fortress Is Our God Verse 1
A mighty fortress is our God<br>
a bulwark never failing<br>
our helper he, amid the flood<br>
of mortal ills prevailing<br>
For still our ancient foe<br>
does seek to work us woe<br>
his craft and power are great<br>
and armed with cruel hate<br>
on earth is not his equal<br>

## A Mighty Fortress Is Our God Verse 2
Did we in our own strength confide<br>
our striving would be losing<br>
were not the right Man on our side<br>
the Man of God's own choosing<br>
You ask who that may be<br>
Christ Jesus, it is he<br>
Lord Sabaoth his name<br>
from age to age the same<br>
and he must win the battle<br>

## A Mighty Fortress Is Our God Verse 3
And though this world, with devils filled<br>
should threaten to undo us<br>
we will not fear, for God has willed<br>
his truth to triumph through us<br>
The prince of darkness grim<br>
we tremble not for him<br>
his rage we can endure<br>
for lo! his doom is sure<br>
one little word shall fell him<br>

## A Mighty Fortress Is Our God Verse 4 (Last)
That Word above all earthly powers<br>
no thanks to them abideth<br>
the Spirit and the gifts are ours<br>
through him who with us sideth<br>
Let goods and kindred go<br>
this mortal life also<br>
the body they may kill<br>
God's truth abideth still<br>
his kingdom is forever<br>
<span class="songkey">G</span>



## I Chose To Follow Verse 1
I choose to follow<br>
I choose to let You lead<br>
With childlike faith I'll walk each day<br>
Knowing that You're all I need<br>
I choose to love You<br>
Because You've chosen me<br>
Of all the things that I could choose to do<br>
I choose to follow You<br>

## I Chose To Follow Verse 1
I'll obey and serve You<br>
I'll obey because I love You<br>
I'll obey,  My life is in Your hands<br>
For it's the way to prove my love<br>
When feelings go away<br>
If it costs me everything<br>
I'll obey<br>

## I Chose To Follow Verse 1
I'll obey and serve You<br>
I'll obey because I love You<br>
I'll obey,  My life is in Your hands<br>
For it's the way to prove my love<br>
When feelings go away<br>
If it costs me everything<br>
I'll obey<br>

## I Chose To Follow Verse 2 (Last)
I choose to follow<br>
I choose to let You lead<br>
With childlike faith I'll walk each day<br>
Knowing that You're all I need<br>
I choose to love You<br>
Because You've chosen me<br>
Of all the things that I could choose to do<br>
I choose to follow You<br>
<span class="songkey">D</span>



## Take My Life and Let It Be Verse 1
Take my life and let it be<br>
consecrated, Lord, to thee<br>
Take my moments and my days<br>
let them flow in endless praise<br>
let them flow in endless praise<br>

## Take My Life and Let It Be Verse 2
Take my hands and let them move<br>
at the impulse of thy love<br>
Take my feet and let them be<br>
swift and beautiful for thee<br>
swift and beautiful for thee<br>

## Take My Life and Let It Be Verse 3
Take my voice and let me sing<br>
always, only, for my King<br>
Take my lips and let them be<br>
filled with messages from thee<br>
filled with messages from thee<br>

## Take My Life and Let It Be Verse 4
Take my silver and my gold<br>
not a mite would I withhold<br>
Take my intellect and use<br>
every power as thou shalt choose<br>
every power as thou shalt choose<br>

## Take My Life and Let It Be Verse 5
Take my will and make it thine<br>
it shall be no longer mine<br>
Take my heart it is thine own<br>
it shall be thy royal throne<br>
it shall be thy royal throne<br>

## Take My Life and Let It Be Verse 6 (Last)
Take my love; my Lord, I pour<br>
at thy feet its treasure store<br>
Take myself, and I will be<br>
ever, only, all for thee<br>
ever, only, all for thee<br>
<span class="songkey">D</span>


## Communion

For I received from the Lord what I also passed on to you:<br><br>
The Lord Jesus, on the night he was betrayed, took bread, and when he had given thanks, he broke it and said, "This is my body, which is for you; do this in remembrance of me."<br><br>
In the same way, after supper he took the cup, saying, "This cup is the new covenant in my blood; do this, whenever you drink it, in remembrance of me."<br><br>
For whenever you eat this bread and drink this cup, you proclaim the Lord's death until he comes.

## Talking Time


[lectionary](https://lectionary.library.vanderbilt.edu/texts/?y=384&z=e&d=16)