---
title: "Trinity Sunday"
output:
  slidy_presentation:
    css: slide-style.css
---
  

```{r, include=FALSE}
knitr::opts_knit$set(root.dir = '../../') 
```

   
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

## Filled with Your Glory Verse 1
In my heart, in my heart<br>
there's a fire burning<br>
A passion deep within my soul<br>
Not slowing down, not growing cold<br>
An unquenchable flame<br>
that keeps burning brighter<br>
A love that's blazing like the sun<br>
For who You are and what You've done<br>
And as the fire is raging on<br>
So Your praise becomes my song<br>

## Filled with Your Glory Chorus 
The whole earth<br>
Is filled with Your glory, Lord<br>
Angels and men adore<br>
Creation longs for what's in store<br>
May You be<br>
Honored and glorified<br>
Exalted and lifted high<br>
Here at Your feet I lay my life<br>

## Filled with Your Glory Verse 2
From the ends of the earth<br>
To the heights of Heaven<br>
Your glory, Lord, is far and wide<br>
Through history You reign on high<br>
From the depths of the sea<br>
To the mountain's summit<br>
Your power, Lord, it knows no bounds<br>
A higher love cannot be found<br>
So let the universe proclaim<br>
Your great power and Your great name<br>


## Filled with Your Glory Chorus 
The whole earth<br>
Is filled with Your glory, Lord<br>
Angels and men adore<br>
Creation longs for what's in store<br>
May You be<br>
Honored and glorified<br>
Exalted and lifted high<br>
Here at Your feet I lay my life<br>

## Filled with Your Glory Chorus  (Last)
The whole earth<br>
Is filled with Your glory, Lord<br>
Mountains bow and oceans roar<br>
Creation longs for what's in store<br>
May You be<br>
Honored and glorified<br>
Exalted and lifted high<br>
Here at Your feet I lay my life<br>
<span class="songkey"></span>



## Tis So Sweet to Trust In Jesus Verse 1
'Tis so sweet to trust in Jesus<br>
and to take him at his word<br>
just to rest upon his promise<br>
and to know, "Thus saith the Lord."<br><br>

Jesus, Jesus, how I trust him<br>
How I've proved him o'er and o'er<br>
Jesus, Jesus, precious Jesus<br>
O for grace to trust him more<br>

## Tis So Sweet to Trust In Jesus Verse 2
O how sweet to trust in Jesus<br>
just to trust his cleansing blood<br>
and in simple faith to plunge me<br>
neath the healing, cleansing flood!<br><br>

Jesus, Jesus, how I trust him<br>
How I've proved him o'er and o'er<br>
Jesus, Jesus, precious Jesus<br>
O for grace to trust him more<br>

## Tis So Sweet to Trust In Jesus Verse 3 (Last)
Yes, 'tis sweet to trust in Jesus<br>
just from sin and self to cease<br>
just from Jesus simply taking<br>
life and rest, and joy and peace.<br><br>

Jesus, Jesus, how I trust him<br>
How I've proved him o'er and o'er<br>
Jesus, Jesus, precious Jesus<br>
O for grace to trust him more<br>

<span class="songkey">G</span>


## Communion

For I received from the Lord what I also passed on to you:<br><br>
The Lord Jesus, on the night he was betrayed, took bread, and when he had given thanks, he broke it and said, "This is my body, which is for you; do this in remembrance of me."<br><br>
In the same way, after supper he took the cup, saying, "This cup is the new covenant in my blood; do this, whenever you drink it, in remembrance of me."<br><br>
For whenever you eat this bread and drink this cup, you proclaim the Lord's death until he comes.

## Talking Time


[lectionary](https://lectionary.library.vanderbilt.edu/texts/?y=384&z=p&d=52)