---
title: "Proper 7"
output:
  slidy_presentation:
    css: slide-style.css
---
  

```{r, include=FALSE}
knitr::opts_knit$set(root.dir = '../../') 
```

   
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```
## All Who Are Thirsty Verse 1
<span class="songkey">G</span>
All who are thirsty<br>
All who are weak<br>
Come to the fountain<br>
Dip your heart in the stream of life<br><br>

Let the pain and the sorrow<br>
Be washed away<br>
In the waves of His mercy<br>
As deep cries out to deep<br><br>

Come Lord Jesus come<br>
Come Lord Jesus come<br>

## All Who Are Thirsty Verse 2 (Last)
All who are thirsty<br>
All who are weak<br>
Come to the fountain<br>
Dip your heart in the stream of life<br><br>

Let the pain and the sorrow<br>
Be washed away<br>
In the waves of His mercy<br>
As deep cries out to deep<br><br>

Come Lord Jesus come<br>
Come Lord Jesus come<br>
Come Lord Jesus come<br>
Come Lord Jesus come<br>


## A Mighty Fortress Is Our God Verse 1
<span class="songkey">G</span>
A mighty fortress is our God<br>
a bulwark never failing<br>
our helper he, amid the flood<br>
of mortal ills prevailing<br>
For still our ancient foe<br>
does seek to work us woe<br>
his craft and power are great<br>
and armed with cruel hate<br>
on earth is not his equal<br>

## A Mighty Fortress Is Our God Verse 2
Did we in our own strength confide<br>
our striving would be losing<br>
were not the right Man on our side<br>
the Man of God's own choosing<br>
You ask who that may be<br>
Christ Jesus, it is he<br>
Lord Sabaoth his name<br>
from age to age the same<br>
and he must win the battle<br>

## A Mighty Fortress Is Our God Verse 3
And though this world, with devils filled<br>
should threaten to undo us<br>
we will not fear, for God has willed<br>
his truth to triumph through us<br>
The prince of darkness grim<br>
we tremble not for him<br>
his rage we can endure<br>
for lo! his doom is sure<br>
one little word shall fell him<br>

## A Mighty Fortress Is Our God Verse 4 (Last)
That Word above all earthly powers<br>
no thanks to them abideth<br>
the Spirit and the gifts are ours<br>
through him who with us sideth<br>
Let goods and kindred go<br>
this mortal life also<br>
the body they may kill<br>
God's truth abideth still<br>
his kingdom is forever<br>


## 10000 Reasons Chorus
<span class="songkey">D</span>
Bless the Lord O my soul<br>
O my soul<br>
Worship His Holy name<br>
Sing like never before<br>
O my soul<br>
I’ll worship Your Holy name<br>

## 10000 Reasons Verse 1a
The sun comes up<br>
It’s a new day dawning<br>
It’s time to sing Your song again<br>
Whatever may pass<br>
And whatever lies before me<br>
Let me be singing<br>
When the evening comes<br>

## 10000 Reasons Chorus
Bless the Lord O my soul<br>
O my soul<br>
Worship His Holy name<br>
Sing like never before<br>
O my soul<br>
I’ll worship Your Holy name<br>

## 10000 Reasons Verse 2a
You’re rich in love<br>
And You’re slow to anger<br>
Your name is great<br>
And Your heart is kind<br>
For all Your goodness<br>
I will keep on singing<br>
Ten thousand reasons<br>
For my heart to find<br>

## 10000 Reasons Chorus
Bless the Lord O my soul<br>
O my soul<br>
Worship His Holy name<br>
Sing like never before<br>
O my soul<br>
I’ll worship Your Holy name<br>

## 10000 Reasons Verse 3a
And on that day<br>
When my strength is failing<br>
The end draws near<br>
And my time has come<br>
Still my soul will<br>
Sing Your praise unending<br>
Ten thousand years<br>
And then forevermore<br>

## 10000 Reasons Chorus (Last)
Bless the Lord O my soul<br>
O my soul<br>
Worship His Holy name<br>
Sing like never before<br>
O my soul<br>
I’ll worship Your Holy name<br>


## Communion

For I received from the Lord what I also passed on to you:<br><br>
The Lord Jesus, on the night he was betrayed, took bread, and when he had given thanks, he broke it and said, "This is my body, which is for you; do this in remembrance of me."<br><br>
In the same way, after supper he took the cup, saying, "This cup is the new covenant in my blood; do this, whenever you drink it, in remembrance of me."<br><br>
For whenever you eat this bread and drink this cup, you proclaim the Lord's death until he comes.

## Talking Time


[lectionary](https://lectionary.library.vanderbilt.edu/texts/?y=384&z=p&d=61)